---
title: "Marvel Rivals"
output: html_document
date: "2025-01-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro
This is a little personal project of mine. After reading about an intro to bayesian stats and given an example about ping pong win rates varying after a series of games it inspired me to apply it to something I do on the daily, play games. This will be a journal of sorts where I keep track of my games played after every session and update the information and see how it varys from day to day. 

```{r prior to 1/29}
alpha <- 53
beta <- 45
theta <- seq(0,1,length = 100)
prior <- dbeta(theta,alpha,beta)
plot(theta, prior, type = "l", col = "blue", lwd = 2,
     main = "Prior Distribution: Estimated Win Probability",
     xlab = "Win Probability", ylab = "Density")


expected_win_prob <- alpha / (alpha + beta)
text(0.15, max(prior) * 0.8, 
     paste("Expected Win Rate:", round(expected_win_prob, 3)), 
     col = "black", cex = 1, font = 1.2)

```

```{r 1/29}
new_wins <- 1
new_losses <- 2

alpha <- alpha + new_wins
beta <- beta + new_losses

posterior <- dbeta(theta, alpha, beta)

plot(theta, posterior, type = "l", col = "red", lwd = 2, 
     main = "Updated Posterior Distribution 1/29",
     xlab = "Win Probability", ylab = "Density")
lines(theta, prior, col = "blue", lwd = 2, lty = 2)
legend("topright", legend = c("Prior", "Posterior"), col = c("blue", "red"), lwd = 2, lty = c(2,1))

expected_win_prob <- alpha / (alpha + beta)
text(0.15, max(posterior) * 0.8, 
     paste("Expected Win Rate:", round(expected_win_prob, 3)), 
     col = "black", cex = 1, font = 1.2)
```

















